The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2025-02-21 _tex/index.tex
Built site for gh-pages

Participant data comes from a previous study *** . Participants
consisted of preterm neonates born between 25- and 31-weeks gestational
age (GA) who were admitted to the level III NICU at *** . Recruitment
took place over a span of one year, from February 2021 to January 2022,
facilitated by a dedicated research nurse. Parents of eligible infants
were approached by the research nurse prior to discharge from the NICU
to explain the study objectives and seek their consent for
participation. Infants meeting the criteria for inclusion were scanned
for the study if they had already been discharged from the NICU, were in
stable condition, and had reached a term equivalent age of 37 to 44
weeks GA. However, certain exclusion criteria were applied to ensure the
homogeneity and integrity of the study sample: infants were excluded if
there was clinical evidence of a congenital malformation or syndrome, a
TORCH infection, or ultrasound evidence of large parenchymal hemorrhagic
infarction (\textgreater2 cm, Grade 4 intraventricular hemorrhage).

@@

MR imaging was performed on a 3.0 Tesla General Electric Discovery MR750
scanner (scanner software version DV26.0\_R03) equipped with a SREE
Medical Systems (Cleveland, OH) single-channel neonatal head coil
(Table~\ref{tbl-mri}). The scans were conducted at the *** 's MRI
Research Facility. Prior to the scanning procedure, subjects were
carefully prepared by a research nurse. Swaddling and feeding were used
to ensure the comfort and cooperation of the subjects during the scan.
Importantly, no sedatives or invasive markers were utilized throughout
the procedure. Subjects were placed within a specially designed SREE
Medical Systems MRI compatible incubator, which facilitated both safety
and motion minimization. Molded foam was strategically positioned around
the head and body within the incubator to further restrict subject
movement. To protect against potential hearing damage, ear plugs were
employed during the scanning process. Additionally, a pulse oximeter was
affixed to the subject's foot to monitor arterial oxygen saturation and
heart rate throughout the scan.

@@

The raw DICOM files acquired from the scanning procedure were converted
to NIfTI (Neuroimaging Informatics Technology Initiative) format using
Chris Rorden's \texttt{dcmniix} tool
\citep{liFirstStepNeuroimaging2016}. SWI magnitude data files were then
used to create subject-specific brain masks that would not erode the SSS
during QSM processing, an issue faced by our group in the past *** . A
step-by-step summary of the pipeline used is shown in
Figure~\ref{fig-graph}.

>>>>

Participant data comes from a previous study \citep{zhu-etal-cmro2}
(under review). Participants consisted of preterm neonates born between
25- and 31-weeks gestational age (GA) who were admitted to the level III
NICU at BC Women's Hospital. Recruitment took place over a span of one
year, from February 2021 to January 2022, facilitated by a dedicated
research nurse. Parents of eligible infants were approached by the
research nurse prior to discharge from the NICU to explain the study
objectives and seek their consent for participation. Infants meeting the
criteria for inclusion were scanned for the study if they had already
been discharged from the NICU, were in stable condition, and had reached
a term equivalent age of 37 to 44 weeks GA. However, certain exclusion
criteria were applied to ensure the homogeneity and integrity of the
study sample: infants were excluded if there was clinical evidence of a
congenital malformation or syndrome, a TORCH infection, or ultrasound
evidence of large parenchymal hemorrhagic infarction (\textgreater2 cm,
Grade 4 intraventricular hemorrhage).

@@

MR imaging was performed on a 3.0 Tesla General Electric Discovery MR750
scanner (scanner software version DV26.0\_R03) equipped with a SREE
Medical Systems (Cleveland, OH) single-channel neonatal head coil
(Table~\ref{tbl-mri}). The scans were conducted at the BC Children's MRI
Research Facility. Prior to the scanning procedure, subjects were
carefully prepared by a research nurse. Swaddling and feeding were used
to ensure the comfort and cooperation of the subjects during the scan.
Importantly, no sedatives or invasive markers were utilized throughout
the procedure. Subjects were placed within a specially designed SREE
Medical Systems MRI compatible incubator, which facilitated both safety
and motion minimization. Molded foam was strategically positioned around
the head and body within the incubator to further restrict subject
movement. To protect against potential hearing damage, ear plugs were
employed during the scanning process. Additionally, a pulse oximeter was
affixed to the subject's foot to monitor arterial oxygen saturation and
heart rate throughout the scan.

@@

The raw DICOM files acquired from the scanning procedure were converted
to NIfTI (Neuroimaging Informatics Technology Initiative) format using
Chris Rorden's \texttt{dcmniix} tool
\citep{liFirstStepNeuroimaging2016}. SWI magnitude data files were then
used to create subject-specific brain masks that would not erode the SSS
during QSM processing, an issue faced by our group in the past
\citep{weberQuantitativeSusceptibilityMapping2021}. A step-by-step
summary of the pipeline used is shown in Figure~\ref{fig-graph}.
